Powering Hidden Markov Model by Neural Network based Generative Models

### 2019-09-03 manuscript/main.tex
revise 3.3 convergence analysis

    \Qq(\bm{H}^{\mathrm{new}}; \bm{H}^{\mathrm{old}}) &\geq \Qq(\bm{H}^{\mathrm{old}}; \bm{H}^{\mathrm{old}})

@@

  \begin{equation}

@@

  \end{equation}
  Therefore we have the inequality 

@@

  Due to the fact that $KL(p(\ubm{s}, \ubm{\kappa}|\ubm{x}; \bm{H}^{\mathrm{old}})\|p(\ubm{s}, \ubm{\kappa}|\ubm{x}; \bm{H}^{\mathrm{old}}))=0$, we have

>>>>

    \Qq(\bm{\Theta}^{\mathrm{new}}; \bm{H}^{\mathrm{old}}) &\geq \Qq(\bm{\Theta}^{\mathrm{old}}; \bm{H}^{\mathrm{old}}).

@@

  \begin{equation*}

@@

  \end{equation*}
  With the above inequality, and the fact that $\EE_{\hat{p}(\ubm{x}),p(\ubm{s},\ubm{\kappa}| \ubm{x}; \bm{H}^{\mathrm{old}})}\left[p(\ubm{s}, \ubm{\kappa}|\ubm{x}; \bm{H}^{\mathrm{old}})\right]$ is independent of $\bm{H}^{\mathrm{new}}$, we have the inequality 

@@

  Due to the fact that $KL(p(\ubm{s}, \ubm{\kappa}|\ubm{x};
  \bm{H}^{\mathrm{old}})\|p(\ubm{s}, \ubm{\kappa}|\ubm{x};
  \bm{H}^{\mathrm{old}}))=0$, we have
